---
title: "DAV Project"
author: "Nishtha Chaudhary"
date: "1 May 2019"
output: html_document
---


#Installing Required Packages

```{r}
install.packages("tidyverse")
library(tidyverse)  # data manipulation
install.packages("cluster")
library(cluster)    # clustering algorithms
install.packages("factoextra")
library(factoextra)
```

#Importing the data file

```{r cars}
library(readxl)
salesdata<-read_excel("C:/Users/nisht/Downloads/sales.xlsx")
head(salesdata)
salesdata<-salesdata[,-1]

#Remove the missing values
df<-na.omit(salesdata)
summary(salesdata)

```

#data preparation

```{r}
# VIM library for using 'aggr'
install.packages("VIM")
library(VIM)

# 'aggr' plots the amount of missing/imputed values in each column
aggr(salesdata)
```



#compute and visualize the distance matrix

```{r}
dst <- dist(salesdata[1:7,-1],)
dst <- data.matrix(dst)

dim <- ncol(dst)

image(1:dim, 1:dim, dst, axes = FALSE, xlab="", ylab="")

axis(1, 1:dim, salesdata, cex.axis = 0.5, las=3)
axis(2, 1:dim, salesdata, cex.axis = 0.5, las=1)


text(expand.grid(1:dim, 1:dim), sprintf("%0.1f", dst), cex=0.6)


````
#Cluster of k-=2

```{r}

k2 <- kmeans(salesdata, centers = 2, nstart = 25)
str(k2)
  
```

```{r}
k2
```

```{r pressure, echo=FALSE}
fviz_cluster(k2, data = salesdata)
?fviz_cluster()
```


## Executing the same with k=3,4,5,6

```{r}
k3 <- kmeans(salesdata, centers = 3, nstart = 25)
k4 <- kmeans(salesdata, centers = 4, nstart = 25)
k5 <- kmeans(salesdata, centers = 5, nstart = 25)
k6 <- kmeans(salesdata, centers = 6, nstart = 25)
k7 <- kmeans(salesdata, centers = 7, nstart = 25)

```

#Plot to compare

```{r}
# plots to compare
p1 <- fviz_cluster(k2, geom = "point", data = salesdata) + ggtitle("k = 2")
p2 <- fviz_cluster(k3, geom = "point",  data = salesdata) + ggtitle("k = 3")
p3 <- fviz_cluster(k4, geom = "point",  data = salesdata) + ggtitle("k = 4")
p4 <- fviz_cluster(k5, geom = "point",  data = salesdata) + ggtitle("k = 5")
p5 <- fviz_cluster(k6, geom = "point",  data = salesdata) + ggtitle("k = 6")
p6 <- fviz_cluster(k7, geom = "point",  data = salesdata) + ggtitle("k = 7")

```

#Grid plot

```{r pressure, echo=FALSE}
library(gridExtra)
grid.arrange(p1, p2, p3, p4,p5,p6, nrow = 2)
```



#Determining Optimal Clusters

```{r pressure, echo=FALSE}
set.seed(123)

fviz_nbclust(salesdata, kmeans, method = "wss")
```
5 clusters is the optimal number of clusters as it appears to be the bend in the knee

#The average silhouette approach measures the quality of a clustering. That is, it determines how well each object lies within its cluster. A high average silhouette width indicates a good clustering.

```{r pressure, echo=FALSE}
fviz_nbclust(salesdata, kmeans, method = "silhouette")
```
Both the above methods suggesting k=5 as the number of optimal clusters

# Compute k-means clustering with k = 6
```{r }
set.seed(123)
final <- kmeans(salesdata, 6, nstart = 25)
str(final)
```

#Cluster Plot

```{r}
fviz_cluster(final, data = salesdata)
```

#Extract then cluster and add to our original data

```{r}
salesdata %>%
  mutate(Cluster = final$cluster) %>%
  group_by(Cluster) %>%
  summarise_all("mean")

install.packages("xlsx")
library(xlsx)
write.table(salesdata, file ="C:/Users/nisht/Desktop/MITA/DAV/Project/cluster.csv",sep=',')
```

```{r}
plot(salesdata$`Sales$`,salesdata$`GM%`)
```

#Adding Cluster Column to our Original file

```{r}
clusterFile <- cbind(salesdata, clusterNum = final$cluster)
head(clusterFile)
```

#Exporting data

```{r}
install.packages("xlsx")
library(xlsx)
write.table(clusterFile, file="C:/Users/nisht/Desktop/MITA/DAV/Project/clusterFile.csv",sep=',')
```

